LabMate: supporting types for MATLAB

### 2024-03-26 writing/IMEKOWC2024/LabMate/paper.tex
[ writing ] fantasy draft of Section 5

\section{LabMate in action}

@@

GravCalc example again: $t_i$ time ($\mathsf{T}$; in seconds); $v_i$ voltage ($\mathsf{ML}^2\mathsf{T}^{-3}\mathsf{I}^{-1}$; in volt)

>>>>

\section{LabMate in action}
\label{sec:example}

@@

Coming back to the example from \sref{sec:example} again, we can give both \texttt{A} and \texttt{B} more precise types, also taking their physical dimensions into account:
\begin{verbatim}
%> A :: [ i <- 9,  j <- 5 ] (if j == 0 then Q T else Q 1)
%> B :: [ Q TODO; Q TODO; Q TODO; Q TODO; Q TODO; Q TODO ]
\end{verbatim}
This says that the entries in the first column of \texttt{A} are quantities of dimension time $\mathsf{T}$, while all other entries are dimensionless quantities. Meanwhile the entries of \texttt{B} are quantities of dimension \todo{fill in} respectively. LabMate reports that the type of \texttt{C} should be
\begin{verbatim}
%< C :: [ 5 x 1 ] (Q (ML^2T^(-3)I^(-1)))
\end{verbatim}
that is a $5 \times 1$ matrix whose entries are all quantities of dimension $\mathsf{ML}^2\mathsf{T}^{-3}\mathsf{I}^{-1}$. Another possible way to use LabMate is to instead declare that this is the expected type for \texttt{C}, and to leave the type of one of the entries in \texttt{B} as an unknown:
\begin{verbatim}
%> B :: [ Q TODO; Q TODO; ?aTy; Q TODO; Q TODO; Q TODO ]
\end{verbatim}
We can then ask LabMate to solve the \remph{meta variable} \texttt{?aTy}, to which LabMate responds that we must have \todo{\texttt{?aTy} = fill in}. This way the types of LabMate can be used to validate and experiment with the dimensional consistency of the quantities involved.

%GravCalc example again: $t_i$ time ($\mathsf{T}$; in seconds); $v_i$ voltage ($\mathsf{ML}^2\mathsf{T}^{-3}\mathsf{I}^{-1}$; in volt)
